---
title: "How to raise the number of participants?"
author: "Hyunsik Yoo"
date: "4/1/2017"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(grid)
library(gridExtra)
setwd('/home/dbgustlr92/kaggle/edx')
edx_csv <- read.csv('appendix.csv')

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

```
## How many lectures did each institution have?
### The number of course by Institution 
```{r, echo=FALSE}
ggplot(edx_csv, aes(edx_csv$Institution)) + geom_bar(aes(fill=edx_csv$Institution)) +
  xlab('Institution') + ylab('Count') + guides(fill=FALSE)
```

The number of lectures in MIT is greater than Harvard.


## Did the number of lectures increase?
```{r , echo=FALSE}
# The number of course by Year and Subject
harvardX <- edx_csv[edx_csv$Institution=="HarvardX",]
mitX <- edx_csv[edx_csv$Institution!="HarvardX",]
harvard <-ggplot(harvardX, aes(harvardX$Year)) + geom_bar(aes(fill=harvardX$Course.Subject), position='dodge') + xlab('Year') + ylab('Count') + labs(title='Harvard',fill='Institution')

mit <- ggplot(mitX, aes(mitX$Year)) + geom_bar(aes(fill=mitX$Course.Subject), position='dodge') + xlab('Year') + ylab('Count') + labs(title='MIT',fill='Institution')
multiplot(harvard,mit)
```

There isn't lectures about _Scienc, Technology, Engineering and Mathematics_ in Harvard first year. Each institution look like they has a special lecture. The number of _Humanities, History, Design, Religion and Education_ lectures is increased extreamly in __Harvard__. in __MIT__, The number of _Science, Technology, Engineering and Mathematics_ lectures is increased extreamly.

```{r, echo=FALSE}
# The number of course by Subject and Institution
ggplot(edx_csv, aes(edx_csv$Course.Subject)) + geom_bar(aes(fill=edx_csv$Institution)) +
  xlab('Subject') + ylab('Count)') + labs(fill='Institution') +
  theme(text = element_text(size=5), axis.text.x = element_text(angle=0))
```

This graph also means that __Harvard__ forcus on _Humanities, History, Design, Religion and Education_ and __MIT__ forcus on _Science, Technology, Engineering and Mathematics_.


## Posting in Forum and Total Course Hours is affected Certificated?
I was very curious about the factors that affect certification. So I analyzed it using several factors.

* Total Course Hours
* Posted in Forum(%)

### Total Course Hours
First, We analyzed about density of __Total Course Hours__ by Subject.  

#### Density of Total Course Hours by Subject

```{r, echo=FALSE}
# Density of Total Course Hours by Subject  
ggplot(edx_csv, aes(edx_csv$Total.Course.Hours..Thousands., colour=edx_csv$Course.Subject)) + 
  geom_density() + labs(x='Total Course Hours', y='Density', colour='Subject') 
```

There are many lectures that have shorter course hours in _Humanities, History, Design, Religion and Education_. All of lecture shorter than 250. and 90% of lectures shorter than 100.
On the other hand, Lectures on computer science range from short lectures to long lectures.

#### Is Total Course Hours affect certification ratio? 
```{r, echo=FALSE}
ggplot(edx_csv, aes(x=edx_csv$Total.Course.Hours..Thousands., y=edx_csv$X..Certified)) +
  geom_point(colour='grey') + labs(x='Total Course Hours', y='Certified(%)') + geom_smooth()
```

All of  lectures with a _Certification rate_ higher than 10% have less then 70hours.(Blue line is mean of __Certified__.) __Total Course Hours__ affects certain points. The __Certification rate__ is reduced to 5% constantly. However, __Certification rate__ is not affected to lectures that __Total Course Hours__ is greater than 80. 

```{r, echo=FALSE}

# Posting in Forum and Total Course Hours is affected Certificated?
ggplot(edx_csv, aes(edx_csv$Total.Course.Hours..Thousands., edx_csv$X..Posted.in.Forum)) +
  geom_point(aes(colour=edx_csv$X..Certified)) +scale_colour_gradient(high = "green") +
  labs(list(x='Total Course Hours', y='Posted in Forum(%)', colour='Certificated(%)'))
```

This graph also shows that the __Total Course Hours__ affects the __certification rate__. 
And the higher the posting rate, the higher the certification rate. This means that Students get a lot of help from the forums. Also there are lots of useful information on lectures on the forum.


### Do students consider the entire lecture time before start?

```{r, echo=FALSE}
# Relationship between Total Course Hours and Participants
ggplot(edx_csv, aes(x=edx_csv$Total.Course.Hours..Thousands., y=edx_csv$Participants..Course.Content.Accessed.)) +
  geom_point(aes(colour=edx_csv$Course.Subject)) +
  labs(x='Total Course Hours', y='Number of Participants', colour='Subject')
```

Except _Computer Science_ lectures, students consider __Total Course Hours__. There are few participants in very short lectures and few participants in very long lectures. However, There are many participants in some of __Computer Science__ lectures regardless of lecture time.
